---
title: "Week 4 homework assignment"
author: Yufei Sun
date: Sept.24th, 2020
output: github_document
editor_options:
  chunk_output_type: inline
---

## DSI-EDA
## Professor Cassy Dorff

## STEPS:

(1) Read the following article (it is for data purposes!)

NPR "CHART: The Relationship Between Seeing Discrimination And Voting For Trump"
- [link here](https://www.npr.org/2017/08/18/544265493/chart-the-relationship-between-seeing-discrimination-and-voting-for-trump)
- [even more information on the data here](https://www.prri.org/research/americans-views-discrimination-immigrants-blacks-lgbt-sex-marriage-immigration-reform/)

(2) Your goal is to recreate the graphic titled "Perceptions Of Discrimination Track Closely With Voting Against Trump." Data for analysis is in the "week4-hw-data.csv" file. Note that this data is from a different version of the PRRI survey, and the results won't match the NPR graph exactly.

(3) Graphic replication: You should:
1. Create an .rmd file to show your analysis. Write 1 sentence for each block of code, explaining what you do in that line of code.
2. Identify and prepare the variables of interest (you may need to group, summarize, or rename variables to reflect the NPR chart.)
3. Next recreate the graphic using ggplot. Recreate everything *except*:
  - the labels that are on California and Wyoming.
  - the colors (you can choose your own or use the same as the article)
4. This means your plot should have the same labels on the axes, gridlines, etc.
5. Is there anything misleading about the graphic? Why or why not?
6. You can give your colleagues "hints" but do *not* give them the code for reproducing the graphic. That breaks our honor code since I asked you not to do it!

```{r}
#answer
library(ggplot2)
library(scales)
mydata <- read.csv("week4-hw-data.csv")
head(mydata) # check whether the data is imported normally
class(mydata) # data frame
summary(mydata) # get some basic statistical feature of mydata
xx <- mydata$trump # extract the column trump
yy <- mydata$discrim # extract the column discrim
idx1 <- which.max(yy) # get the index of min value in yy
idx2 <- which.min(yy) # get the index of min value in xx
# create a plot and add points
p = ggplot(data = mydata) + geom_point(aes(x=trump, y=discrim), color = '#59A09F', size = 2)
# modify the x axis
p = p + scale_x_continuous(labels = percent, limits=c(0.04, 0.7), breaks=round(seq(from = 0, to = 0.7, by = 0.05),2))
# modify the y axis
p = p + scale_y_continuous(labels = percent, limits=c(0.12,0.9), breaks=round(seq(from = 0.1, to = 0.9, by = 0.05),2)) 
# add labels for the axes
p = p + labs(x="2016 Trump Vote",y="% Saying Discrimination Prevalent")
# change the background color and the grid color, and hide the legend
p = p + theme(legend.position = "none", 
              panel.background = element_rect(alpha(colour = "white", 0.1)),
              panel.grid.major = element_line(alpha(colour = "grey", 0.3)))
# get a linear regression model
model <- lm(mydata$discrim~mydata$trump, mydata)
# show the model
summary(model)
# extract coefficients from the model
co <- model$coefficients
# draw the regression line on the plot
p = p + geom_abline(slope = co[2], intercept = co[1], color = "grey", size = 1, alpha = 0.9)
# add a label for extreme point1
p = p + geom_text(aes(x = xx[idx1], y = yy[idx1], label = "Washington D.C."), size=3, hjust = 0, nudge_x = 0.01)
# add a label for extreme point2
p = p + geom_text(aes(x = xx[idx2], y = yy[idx2], label = "North Dakota"), size=3, hjust = 0, nudge_x = 0.01)
# show the plot
print(p)
```

(4) What do you think about this graphic? Do you think this relationship exists? Why or why not, in your own words?

The graphic above clearly shows the distribution of the two factors——discrimination and voting against Trump. I think data visualized above do not support that "Discrimination Track Closely With Voting Against Trump". The Multiple R-squared of the result of linear regression is too small to be accepted. With naked eyes, the dots are not distributed in the narrow range near the regression line.

(5) Make one additional graphic of your choice using this data. Write 3-5 sentences in clear, plain language about what the graphic illustrates about the data.

```{R}
# answer
colnames(mydata) <- c('X', 'state', 'Voting for Trump', 'Seeing Discrimination')
mydata.long <- pivot_longer(data = mydata, 
             cols = -c('state','X'), 
             names_to = 'Index', 
             values_to = 'ratio')
ggplot(mydata.long, aes(x=ratio, fill = Index)) + 
  geom_histogram(binwidth=.1, alpha=.5, position="identity") + 
  labs(x="Ratio",y="Count", 
       title = "Distribution of Seeing Discrimination And Voting For Trump") + 
  scale_colour_discrete(labels = c('Seeing Discrimination','2016 Voting For Trump'))
```
The histogram above shows that the rates of voting against Trump in the states were concentrated around 50%, and the rates of seeing discrimination in the states were also concentrated around 50%. The extreme values far from the average are few in the two set of values.

## Part 2

Previously, we explored data about wine. 

1. Make a barplot with the wine data to explore our original question about the relationship between alcohol content and quality. Why might a simple bar plot be misleading here? (Read a bit about geom_bar first, if needed)


```{r}
#answer
winequality_red <- read_csv('winequality-red.csv')
head(winequality_red)
wine.long <- pivot_longer(data = winequality_red, 
             cols = c('quality','alcohol'), 
             names_to = 'Index', 
             values_to = 'Value')
ggplot(wine.long, aes(x = Value, fill = Index)) + 
  geom_bar(width = 0.4, alpha=.5, position = 'identity')
```
The units of the two factors are not the same. So it is meaningless even misleading to display the two sets of values of the two factors. Showing the distribution of the two factors in one barplot is not helpful to show the relationship between the two factors.

2. A lot of the hardwork in learning R skills is learning how to read helpfiles and use stackoverflow on your own. I showed you a glimpse of information about themes in class. Use the code below to make additional changes. This might take a bit of digging and reading about these graphical components online. Specifically, can you figure out how to (try to complete 2 out of 4):

* get rid of panel border completely and keep the grid lines?
* put the legend on the top or bottom?
* capitalize the legend name appropriately?
* add units for alcohol content and wine quality (if applicable)?

```{R}
ggplot(winequality_red, aes(x=quality, y= alcohol)) +
      geom_jitter(aes(col=`fixed acidity`)) +
      scale_color_viridis(name = 'Fixed Acidity', option = "D", direction = -1, alpha = .6) + # capitalize the legend name appropriately
      labs(title="Alcohol Content, Fixed Acidity and Wine Quality", y="Alcohol Content", x="Wine Quality")  +
      theme(legend.position = "top") # put the legend on the top  
```


2. Explain in 1-3 sentences what we can learn from our wine graphic produced in class.

Answer: 
1. There are relatively few excellent and very poor wines. Most of wines are of medium quality.
2. There is a negative correlation between the alcohol content and the fixed acidity in red wine.
3. There was no significant correlation between the quality and the alcohol content of red wine.

